---
title: "Data for USGS"
author: "Annie Kellner"
date: "2023-05-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r packages, include=FALSE}

library(dplyr)
library(sf)
library(knitr)
library(adehabitatLT)
library(tmap)
library(tmaptools)
library(lubridate)
library(tidyr)
library(conflicted)

source('./Code/MyFunctions.R')

conflicts_prefer(
  dplyr::select(),
  dplyr::filter()
)

```

```{r, include=FALSE}

rm(list = ls())

```

# BEARS INCLUDED IN STUDY

This study includes a subset of GPS-collared bears that spent ≥ 7 consecutive days on land between June 1 and September 30 of any given year. Bears with insufficient data (< 100 total points) were excluded. In total, our analysis includes tracking data from 21 bear-summers (19 individuals including two bears with data from two separate years) over eight calendar years (2005, 2008-9, 2011 – 2015).  

```{r load-data, include=FALSE}

b <- readRDS('./Data/Derived-data/DFs/bears_ch2_052823.Rds')

```

```{r}

# Create track in adehabitatLT

bsf <- st_as_sf(b, crs = st_crs(3338))
bsf <- dplyr::select(bsf, -c('X','Y'))

bsf <- cbind(bsf, st_coordinates(bsf))

bdf <- bsf %>%
  st_drop_geometry() %>%
  as.data.frame() %>%
  dplyr::select(id, datetime, X, Y) %>%
  na.omit()

ltraj <- as.ltraj(bdf[,c("X","Y")], date=bdf$datetime, id=bdf$id, typeII = TRUE)

summary <- summary(ltraj)

summary$DaysTrack <-round(difftime(summary$date.end, summary$date.begin, units="days"),digits=1)

summary <- summary %>%
  select(id, date.begin, date.end, DaysTrack) %>%
  mutate(year = year(date.begin)) %>%
  mutate(DaysTrack = as.numeric(DaysTrack)) %>%
  arrange(year) 

kable(summary)

```

Summary stats for tracking days are as follows:   
`r summary(summary$DaysTrack)`

# Dividing bears into subgroups

I divided bear movements into two subgroups: 
  1. At the Bonepile
  2. Along the coastal corridor
  
I used NSD analyses to visually observe the 'plateaus' in movement, i.e. when bears stopped traversing the corridor and stayed at or around the bonepile for many days. After visually inspecting the plots, I cross-checked the locations to make sure they were near the bonepile (and not another distant location or denning site). For my analysis, I planned to conduct separate RSF and SSF analyses for the two groups, given their differences in movements and behavior. 

## Used Locations for Corridor Movement
  
```{r}
cor <- b %>%
  filter(at_bonepile == 0)

bon <- b %>%
  filter(at_bonepile == 1)

```



