---
title: "Data for USGS"
author: "Annie Kellner"
date: "2023-05-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r packages, include=FALSE}

library(dplyr)
library(sf)
library(knitr)
library(adehabitatLT)
library(tmap)
library(tmaptools)
library(lubridate)
library(tidyr)

source('./Code/MyFunctions.R')

```

```{r, include=FALSE}

rm(list = ls())

```

This study includes a subset of GPS-collared bears that spent ≥ 7 consecutive days on land between June 1 and September 30 of any given year. Bears with insufficient data (< 100 total points) were excluded. In total, our analysis includes tracking data from 21 bear-summers (19 individuals including two bears with data from two separate years) over eight calendar years (2005, 2008-9, 2011 – 2015). ADD DAYS TRACKED  

```{r load-data, include=FALSE}

b <- readRDS('./Data/Derived-data/DFs/bears_ch2_052823.Rds')

```

```{r}

# Create track in adehabitatLT

bsf <- st_as_sf(b, crs = st_crs(3338))
bsf <- dplyr::select(bsf, -c('X','Y'))

bsf <- cbind(bsf, st_coordinates(bsf))

bdf <- bsf %>%
  st_drop_geometry() %>%
  as.data.frame() %>%
  dplyr::select(id, datetime, X, Y) %>%
  na.omit()

ltraj <- as.ltraj(bdf[,c("X","Y")], date=bdf$datetime, id=bdf$id, typeII = TRUE)

summary <- summary(ltraj)

summary$DaysTrack <-round(difftime(summary$date.end, summary$date.begin, units="days"),digits=1)
summary <- dplyr::select(summary, id, date.begin, date.end, DaysTrack)
summary

```


