---
title: "Space_Use_Summaries_Ch2"
author: "Annie Kellner"
date: "2022-09-15"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}

library(dplyr)
library(sf)

rm(list = ls())

#knitr::opts_chunk$set(echo = TRUE)

```


```{r load-and-prep-data, include=FALSE}

pb <- readRDS('./Data/bears_092921.Rds')

pb2 <- pb %>%
  mutate(bear_type = case_when(
    id == "pb_20525.2013" | id == "pb_20525.2014" | id == "pb_20586.2008" | 
      id == "pb_32366.2014" ~ "bp_only",
    id == "pb_32255.2008" | id == "pb_pb_21237.2011" | id == "pb_20418.2005" | 
      id == "pb_20414.2009" ~ "natural",
    TRUE ~ "bonepile"
  ))

# Individual bears

ind <- pb2 %>%
  st_drop_geometry() %>%
  group_by(id) %>%
  slice_head() 

```

Upon completing the NSD analysis and visually inspecting each interactive plot, I divided the bears into three categories:

  * Coast & Bonepile Bears = Bears with 'dispersing' NSD patterns
    + These bears typically arrive on land and travel along the coast to the bonepile,
    | or arrive at the bonepile and then travel along the coast after they leave
    
  * Bonepile-only Bears = Bears with 'home range' NSD patterns
    + These bears arrive at the bonepile and do not leave for the duration of the study
    
  * Coast Bears = Bears who do not visit any bonepiles
    + These bears can exhibit any type of NSD pattern

The breakdown of individuals who fall into these categories is: 

```{r echo=FALSE}

table(ind$bear_type)

```



